Replacing standard galaxy profiles with \\ mixtures of Gaussians

### 2012-10-20 documents/mixtures/mixture_models.tex
notes to self

The performance advantages we will obtain from using mixtures of
Gaussians are not simply that convolution itself is trivial.  The
standard unconvolved galaxy models, especially the de~Vaucouleurs and
S\'ersic models (\citealt{dev}, \citealt{ser}), are very ill-behaved
near the galaxy center.  Rendering these profiles precisely near the
center can be very challenging numerically.  In addition, most of the
rendering time is spent at very small radii, where PSF convolution is
going to erase all structure anyway.  That is, a mixture-of-Gaussians
description of the de~Vaucouleurs profile saves time both in rendering
\emph{and} in PSF convolution; it produces profiles that are
approximate but very high performance when all real uses of the
profiles are PSF-convolved, as they usually are.

@@

...make recommendations: Use the $M^{\lux}=6$ lux and the $M^{\luv}=8$
luv!...

@@

...pegagogical figure demonstrating these operations and their results...

...what about mixtures of exps and devs:  No problem!...

>>>>

... insert here a paragraph about the \emph{wisdom} of fitting these
standard profiles: When is it scientifically okay?...

The performance advantages we will obtain from using
mixture-of-Gaussian approximations are not simply that convolution
itself is trivial.  The standard unconvolved galaxy models, especially
the de~Vaucouleurs and S\'ersic models (\citealt{dev}, \citealt{ser}),
are very ill-behaved near the galaxy center.  Rendering these profiles
precisely near the center can be very challenging numerically.  In
addition, most of the rendering time is spent at very small radii,
where PSF convolution is going to erase all structure anyway.  That
is, a mixture-of-Gaussians description of the de~Vaucouleurs profile
saves time both in rendering \emph{and} in PSF convolution; it
produces profiles that are approximate but very high performance when
all real uses of the profiles are PSF-convolved, as they usually are.

@@

... make recommendations: Use the $M^{\lux}=6$ lux and the $M^{\luv}=8$
luv!...

@@

... pegagogical figure demonstrating these operations and their results...

... what about mixtures of exps and devs:  No problem!...

... finally: The insights that \emph{could} be gained by interrogating
these profile approximations in three dimensions...!
